Review stages

### 2024-04-10 doc/review-stages.qmd
Added next stage with a list of screened papers.

```{r tbl-titles-kept}
#| tbl-cap: "Number of articles each reviewer kept after the first screening of the titles."
title_reviews |>
  map(\(df) count(df, name = "Articles kept")) |>
  list_rbind(names_to = "Reviewers") |>
  # TODO: Include percent of total articles.
  knitr::kable()
```

@@

```{r}
common_titles <- title_reviews |>
  reduce(\(df1, df2) {
    inner_join(df1, df2, by = join_by(id, title, publication_date, doi))
  })
```

@@

One person will review and flag any o might be relevant but are not in
agreement to keep.

@@

@@

@@

-   first us reading a few to get an idea of themes and information to
    extract
-   and then discuss together the themes to group by and information to
    extract
-   Then we follow what we agreed on

@@

-   How to visualize?

>>>>

```{r tbl-titles-kept}
#| message: false
#| tbl-cap: "Number of articles each reviewer kept after the first screening of the titles."
title_reviews |>
  map(\(df) count(df, name = "Articles kept")) |>
  list_rbind(names_to = "Reviewers") |>
  # TODO: Include percent of total articles.
  knitr::kable()
```

@@

```{r}
common_titles <- title_reviews |>
  reduce(\(df1, df2) {
    inner_join(df1, df2, by = join_by(id, title, publication_date, doi))
  })

#| tbl-cap: "Number of articles we all agreed on."
common_titles |>
  count(name = "Titles all agreed on") |>
  knitr::kable()

```

@@

One person will review the titles and flag any paper that might be
relevant but are not in agreement to keep.

@@

We saved a new csv file with all the disagreements and saved a new list
called "resolved.csv" where the final papers to include are listed.

```{r csv-paper-disagreements}

title_disagrements <- title_reviews |>
  map(\(df) anti_join(df, common_titles, by = join_by(id, title, publication_date, doi))) |>
  list_rbind() |>
  distinct()

#save new csv file to go through links and check disagreements
write.table(title_disagrements, file = here("data/review/titles/disagreements.csv"))

```

@@

-   all will review the abstracts of the included papers
-   this will create our final list of included papers

@@

-   first skimming the papers and group by themes
-   then read a few from each theme to decide on what information to
    extract
-   then discuss together the themes to group by and information to
    extract
-   then we follow what we agreed on

@@

-   how to visualize?
